### 2024-11-24 manuscript.tex
Update on Overleaf.

Absolute calibration of the observed backscatter was performed by comparing the
measured clear-sky molecular backscatter statistically with simulated clear-sky
molecular backscatter. AVBC was resampled to 5 min temporal resolution and 50 m
vertical resolution to increase signal-to-noise ratio while having enough
resolution to detect small-scale cloud variability. The noise standard
deviation was calculated from AVBC at the highest range, where no clouds are
expected.  A cloud mask was calculated from AVBC using a fixed threshold of
$\mathrm{2\times 10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard
deviations of range-scale noise. Fig. \ref{fig:example}b shows an example of
simulated Vaisala CL51 backscatter from ERA5 data, corresponding to a day of
measurements by the instrument on the PS81/3 voyage.

@@

Here, we use a free-running (i.e., \emph{not} nudged or using prescribed SST)
coupled GSRM simulation made for the purpose of climate projection.  nextGEMS
has so far produced four cycles of model runs. We used a Cycle 3 run
\emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b} for a model
time period of 20 January 2020 to 22 July 2025, of which we analysed the full
years 2021--2024 (inclusive). While a Cycle 4 run was available, we could not
use it due to the unavailability of the necessary variables. The horizontal
resolution of ngc3028 is about 5 km.  The model output is available on 90
vertical levels and 3-hourly instantaneous temporal resolution.  Unlike current
general circulation models (GCMs), the storm-resolving version of ICON does not
use convective and cloud parameterization but relies on explicit simulation of
convection and clouds on the model grid. While this makes the code development
simpler without having to rely on uncertain parameterizations, it can miss
smaller-scale clouds below the grid resolution.  Turbulence and cloud
microphysics are still parameterized in this model.

>>>>

Absolute calibration of the observed backscatter was performed by comparing the
measured clear-sky molecular backscatter statistically with simulated clear-sky
molecular backscatter. AVBC was resampled to 5 min temporal resolution and 50 m
vertical resolution to increase signal-to-noise ratio while having enough
resolution to detect small-scale cloud variability. The noise standard
deviation was calculated from AVBC at the highest range, where no clouds are
expected.  A cloud mask was calculated from AVBC using a fixed threshold of
$\mathrm{2\times 10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard
deviations of range-scaled noise. Fig. \ref{fig:example}b shows an example of
simulated Vaisala CL51 backscatter from ERA5 data, corresponding to a day of
measurements by the instrument on the PS81/3 voyage.

@@

Here, we use a free-running (i.e., \emph{not} nudged or using prescribed SST)
coupled GSRM simulation made for the purpose of climate projection.  nextGEMS
has so far produced four cycles of model runs. We used a Cycle 3 run
\emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b} for a model
time period of 20 January 2020 to 22 July 2025, of which we analysed the period 2021--2024 (inclusive). While a Cycle 4 run was available, we could not
use it due to a lack of availability of the necessary variables. The horizontal
resolution of ngc3028 is about 5 km.  The model output is available on 90
vertical levels and 3-hourly instantaneous temporal resolution.  Unlike current
general circulation models (GCMs), the storm-resolving version of ICON does not
use convective and cloud parameterization but relies on explicit simulation of
convection and clouds on the model grid. While this makes the code development
simpler without having to rely on uncertain parameterizations, it can miss
smaller-scale clouds below the grid resolution.  Turbulence and cloud
microphysics are still parameterized in this model.
